---
title: "Presentation of the results"
output:
  pdf_document: default
  html_notebook: default
  
always_allow_html: true
---

This is the presentation of the partial results of the study so far.
It is a Rmarkdown document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First let's setup the code.
```{r, include=FALSE}
library("here")
source(here("code","packages.R"))
source(here("code","functions.R"))
```

```{r environment_set_up, include=FALSE}
# Préparation de l'environnement
tar_visnetwork(targets_only = TRUE)
```

Start the targets.

```{r include=FALSE}
tar_make()
```

# The Palmer Penguins data
Show me a glimpse of the Palmer Penguins dataframe
```{r}
penguins_df <- tar_read(penguins_df)
# take a look at the data
glimpse(penguins_df)
# remove all the cases with NAs 
f_penguins_df <- tar_read(fpenguins_df)
glimpse(f_penguins_df)
```
## Show me the species in a plotbar
```{r}
# do a barplot with the species
tar_read(species_bar_plot)
```

## Correlation matrix
```{r}
# do a correlation matrix
tar_read(correlation_mx)
```

## Species VS size
```{r}
# do a scatter plot species vs size
# add a linear model line
tar_read(species_size_cp) + geom_smooth(method = "lm")
# as one can, see there's a positive linear correlation between the body mass and the flipper length
```

## This sounds interesting, let's create a linear model to predict body mass from the specimen's flipper length 
```{r}
# build the model to predict the body mass from the flipper length
model <- tar_read(model_bm_fl)
model
summary(model)
```
## Now let's create a dataframe with the actual values and the predictions from our model
```{r}
# create a df with the real values, the residuals and the prediction
model_df <- tar_read(model_bm_fl_df)
print(as_tibble(model_df))
```

## Conclusion
This ends the short analysis and presentation of the Palmer Penguins dataframe.
