---
title: "results"
format: html
editor: visual
---

## Presentation

This is the presentation of the partial results of the study so far. It is a Quarto document.

## The code

Let's start by loading the code.

```{r}
library("here")
source(here("code","packages.R"))
source(here("code","functions.R"))
```

## Targets

Start your targets.

```{r}
tar_make()
tar_visnetwork(targets_only = TRUE)
```

## Palmer Penguins dataframe

Show me a glimpse of the Palmer Penguins dataframe.

```{r}
penguins_df <- tar_read(penguins_df)
# if you want take a look at the data
# glimpse(penguins_df)
# remove all the cases with NAs 
f_penguins_df <- tar_read(fpenguins_df)
glimpse(f_penguins_df)
```

## Species

Show me the species in a plotbar.

```{r}
tar_read(species_bar_plot)
```

## Correlation matrix

Make a correlation matrix.

```{r}
tar_read(correlation_mx)
```

## Species VS size

Build a scatter plot species vs size and add a linear model line.

```{r}
tar_read(species_size_cp) + geom_smooth(method = "lm")
```

As one can, see there's a positive linear correlation between the body mass and the flipper length.

## Creating a linear model

This sounds interesting, let's create a linear model to predict body mass from the specimen's flipper length .

```{r}
# build the model to predict the body mass from the flipper length
model <- tar_read(model_bm_fl)
model
summary(model)
```

## Checking the predicted values

Now let's create a dataframe with the actual values and the predictions from our model.

```{r}
# create a df with the real values, the residuals and the prediction
model_df <- tar_read(model_bm_fl_df)
print(as_tibble(model_df))
```

## Conclusion

This ends the short analysis and presentation of the Palmer Penguins dataframe.
